%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Chris West} \\ %\vspace{1pt}
    %123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 905-469-4104 ~ \href{mailto:christinewwwest@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{christinewwwest@gmail.com}} ~ 
    \href{https://https://www.linkedin.com/in/chris-west-code-wrangler///}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://https://github.com/Westc13/}{\raisebox{-0.2\height}\faGithub\ \underline{github}}
    \vspace{-8pt}
\end{center}



%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
    %\resumeSubHeadingListStart
        %\begin{multicols}{4}
            %\begin{itemize}[itemsep=-5pt, parsep=3pt]
                %\item\small Data Structures
                %\item Software Methodology
                %\item Algorithms Analysis
                %\item Database Management
                %\item Artificial Intelligence
                %\item Internet Technology
                %\item Systems Programming
                %\item Computer Architecture
            %\end{itemize}
        %\end{multicols}
        %\vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Working knowledge}{: Python, JS/TS, React, HTML/CSS, Tailwind, SQL, Git/GitHub, Linux, Firebase, Contentful CMS, Jira/Kanban} \\
% \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
     \textbf{Exposure}{: Ruby, C\verb|#|, C, LaTex} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {McMaster University}{Mar -- Apr 2023}
      {Web Developer, Contract}{Hamilton, ON}
      \resumeItemListStart
        \resumeItem{Developed and maintained a research facility website using React.js, SCSS, and Contentful CMS, utilizing Git and GitHub for version control and Jira with a Kanban board for collaboration.}
        \resumeItem{Ensured website accessibility compliance with WCAG 2.1 guidelines, optimized website performance, and improved website visibility through SEO techniques.}
        \resumeItem{Successfully launched the website on time and within budget, after conducting thorough testing for accessibility, SEO, and performance, resulting in positive feedback from users and stakeholders.}
        %\resumeItem{Explored ways to visualize and send a daily report of test results to team members  using HTML, Javascript, and CSS.}
      \resumeItemListEnd

    \resumeSubheading
      {CoLab}{Oct 2022 -- Jan 2023}
      {Software Developer, Intern}{GTA, ON}
      \resumeItemListStart
        \resumeItem{Collaborated on an international cross-functional team to launch a live product using Agile methodologies, Trello boards, and weekly standups, working closely with a Product Manager, Product Designer, and Developers.}
        \resumeItem{Developed product features using React and design tools such as Figma, based on requirements, design specifications, and user feedback.}
        \resumeItem{Incorporated user feedback to improve the product's features and functionality and participated in the final live demo of the project to stakeholders.}
        %\resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RxStar} $|$ \emph{Python, React,PostGreSQL, AWS}}{May - Present 2023}
          \resumeItemListStart
            \resumeItem{Developing a medication and food/drink interaction web app using React, Python, PostgreSQL, and AWS.}
            \resumeItem{Implemented frontend UI components and backend APIs to facilitate medication and food/drink scheduling while avoiding interactions.}
            \resumeItem{Integrated a drug interaction database/API, ensuring data security and collaborating with medical professionals to provide accurate information.}
            %\resumeItem{Used Cron to schedule the program to execute automatically at 11 AM every morning so a reservation is made for me.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{NBRLYU} $|$ \emph{React, Firebase, HTML/CSS}}{Oct 2022 - Jan 2023}
          \resumeItemListStart
            \resumeItem{Developed a web application facilitating acts of kindness among neighbors, reducing loneliness and fostering community engagement.}
            \resumeItem{Utilized technologies such as React, Firebase, and HTML/CSS to create a user-friendly interface for posting requests and offers of assistance.}
            \resumeItem{Implemented features like notifications, user profiles, and activity tracking to enhance user experience and promote a sense of belonging within neighborhoods.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{4-U-2-Write} $|$ \emph{React, Firebase, HTML/CSS}}{Aug - Sept 2022}
          \resumeItemListStart
            \resumeItem{Created a user-friendly SPA that offered a customizable timer, writing prompts, and a clean interface to enhance focus and productivity.}
            \resumeItem{Designed a timer feature with a 15-second inactivity warning, promoting consistent writing engagement. Integrated a communal daily writing prompt for users to contribute and engage with the writing community.}
            \resumeItem{Implemented robust error handling and integrated APIs for writing prompts. Added light and dark mode options for enhanced user customization.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Juno College}{Jun -- Sep 2022}
      {Web Development Immersive Diploma}{Toronto, ON}
  %\resumeSubHeadingListEnd
%\resumeSubHeadingListStart
    \resumeSubheading
      {Toronto Metropolitan University}{Sep 2002 -- May 2005}
      {Bachelor of Science in Food and Nutrition}{Toronto, ON}
  \resumeSubHeadingListEnd


%-----------INVOLVEMENT---------------
\section{Awards / Achievements}

\begin{itemize}
\item \textbf{Publication:} The Canadian Journal of Gastroenterology (Feb 2009)
\item \textbf{Bronze Medal:} Council for Continuing Pharmaceutical Education Accreditation (Sep 2011)
\end{itemize}

\end{document}
